Founder allele effects for hotspot traits

### 2019-08-19 analysis/paper/preliminary/allele-effects-exploration.Rmd
added partitions fctn

>>>>

## Calculate all partitions & contrasts

```{r}
pp <- partitions::setparts(8) %>% as.matrix() # 8 founder lines
dim(pp)
# calculate set of contrasts for a single group_assignments vector
calculate_contrasts <- function(group_assignments, effects_vector){
  if (max(group_assignments) == 1){
    stop("group_assignments vector must have at least one entry greater than 1.")
  }
  n <- max(group_assignments) # n subsets constitute the partition.
  ncontr <- choose(n, 2) # we'll always compare pairs of subsets as contrasts
  # calculate the rowwise means for each of n groups
  means <- numeric(length = n) # one mean per founder allele
  for (i in 1:n){
    means[i] <- mean(effects_vector[which(group_assignments == i)])
  }
  combn(n, 2) -> cmat # indices for contrasts
  out <- apply(X = cmat, MARGIN = 2, FUN = function(x){abs(means[x[1]] - means[x[2]])})
  mynames <- list()
  for (i in 1:n){
    mynames[[i]] <- paste(LETTERS[which(group_assignments == i)], collapse = "")
  }
  for (i in 1:ncontr){
    names(out)[i]<- paste(mynames[cmat[, i]], collapse = "_")
  }
  return(out)
}
effects_mat <- local_nonlocal_annot %>%
  ungroup() %>%
  select(cA:cH) %>%
  as.matrix()
```

```{r}
list(
  calculate_contrasts(pp[,4001], effects_vector = as.numeric(effects_mat[1, ])),
  calculate_contrasts(pp[,4000], effects_vector = as.numeric(effects_mat[1, ]))
)
```
